% !TeX spellcheck = en_US
\input{template.tex}
\hypersetup{
	pdftitle={The Title of the Bachelor Thesis},
	pdfauthor={Lukas Winkler}
}
\title{The Title of the Bachelor Thesis}
\subtitle{bla bla}
\author{Lukas Winkler\footnote{\texttt{a01505981@unet.univie.ac.at}}}
%\publishers{TEST}
\date{1. August 2019}

\usepackage{lipsum}  % just for lorem ipsum
\newcommand{\blabla}{Bla bla bla}

\begin{document}
	
\maketitle

\tableofcontents

\chapter{Introduction}\label{introduction}


Here comes some short science explanation about how planets form and water is transported.


\section{The perfect merging assumption}

To better understand how this process works, large n-body simulations over the lifetime of the solar systems have been conducted.\todo{give an example} Most of these neglect the physical details of collisions when two bodies collide for simplicity and instead assume that a perfect merging occurs. So all the mass of the two progenitor bodies and especially all of their water (ice) is retained in the newly created body. Obviously this is a simplification as in real collisions perfect merging is very rare and most of the time either partial accretion or a hit-and-run encounter occurs. (\cite{CollisionTypes}) Therefore the amount of water retained after collisions is consistently overestimated in these simulations. Depending on the parameters like impact angle and velocity a large fraction of mass and water can be lost during collisions.\footcite{MaindlSummary}

\section{Some other heading}

To understand how the water transport works exactly one has to find an estimation of the mass and water fractions that are retained during two-body simulations depending on the parameters of the impact.

\todo{And here the explanation of the chapters}


\include{20_simulations}

\include{30_results}

\include{40_interpolations}

\appendix

\chapter{Mass retention}

\todo[inline]{Just mention quickly that everything can also be applied to mass retention and show a few plots}



\chapter{Placeholder}


\nocite{*}

\printbibliography


\end{document}

